Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2017-01-04 documents/437Slides/slides.tex
slides for 437 talk

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1,2}}
\institute
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada \\
    \inst{2}%
    University of Waterloo\\
    Ontario, Canada \\
}
\date[QN 2016]{Quantum Networks Workshop, IIP, Nov. 2016}

@@

\begin{frame}
    \titlepage
    \note[item]{Thank International Institute for Physics (IIP) for support}
    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
\end{frame}

\begin{frame}
    \frametitle{The Triangle Scenario (TS)}
    \begin{center}
        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
    \note[item]{Triangle Scenario has be studied extensively before}
    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}
    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
\end{frame}

\begin{frame}
    \frametitle{This Talk}
    \begin{enumerate}
        \item Inflation technique provides polynomial inequalities
        \item Inequalities witnessing non-local quantum correlations in the Triangle Scenario
        \item Discuss search for new non-local quantum correlations
    \end{enumerate}
    \note[item]{This talk is going to have three components}
    \note[item]{Demonstrating how something called the inflation technique allows one derive polynomial compatibility constraints for and causal structure}
    \note[item]{Using the inflation technique to find inequalities that demonstrate non-local quantum distributions on the Triangle scenario}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \vfill
    \begin{center}
        Triangle Scenario
    \end{center}
    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    \vfill
    \begin{center}
        \noindent\rule{8cm}{0.4pt}
    \end{center}
    \vfill
    \begin{center}
        General Setting
    \end{center}
    \begin{align*}
    \mscenario &= \bc{V_1, \ldots, V_n} \\
    \prob^{\mscenario} &= \bc{\prob[V_1], \ldots, \prob[V_n]}
    \end{align*}
    \[ \forall V \in \mscenario: \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
    \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
    \vfill
\end{frame}

\section{Part 1: Inflation Technique}
\begin{frame}
    \frametitle{Demonstrating Inflation Technique}
    \vfill
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
    \end{columns}
    \end{center}
    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Some Inflations of the Triangle Scenario}
    \begin{center}
    \begin{tabular}{cc}
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
        \\
        %\hline
        The Triangle Scenario
        &
        Spiral Inflation \\
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
        \\
        %\hline
        Cut Inflation
        &
        Large Inflation \\
        %\hline
    \end{tabular}
    \end{center}
\end{frame}

>>>>

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1,2}}
\institute
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada \\
    \inst{2}%
    University of Waterloo\\
    Ontario, Canada \\
}
\date[Phys 437 2017]{Phys 437 Oral Report, Jan. 2017}

@@

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}
    \frametitle{This Talk}
    \begin{enumerate}
        \item Motive why quantum-classical difference is worth studying
        \item Explain why the triangle scenario is interesting
        \item Briefly discuss how we obtained new measures of non-classicality
        \item Discuss search for new non-classical quantum correlations
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Quantum/Classical Discrepancies}
    \textbf{Quantum Mechanics can do stuff that Classical Mechanics can't!}
    \begin{itemize}
        \item Quantum Information/Communication
        \begin{itemize}
            \item Quantum Key Distribution (QKD)
        \end{itemize}
    \end{itemize}
    \begin{itemize}
        \item Quantum Algorithms/Computation
        \begin{itemize}
            \item Shor's Algorithm, Quantum Simulated Annealing, String Matching, \ldots
            \item Polynomial or even exponential advantage
            \item \url{http://math.nist.gov/quantum/zoo/}
        \end{itemize}
    \end{itemize}
    \begin{itemize}
        \item Quantum Foundations
        \begin{itemize}
            \item Derivation of Bell inequalities
            \item Abandoning local hidden variable theories (LHVs)
        \end{itemize}
    \end{itemize}
    \textbf{Important to determine \textit{precisely} where quantum/classical differ, but how?}
\end{frame}

\begin{frame}
    \frametitle{Notation \& Jargon}
    \begin{center}
        Which observations are \textit{compatible} with a given classical model?
    \end{center}
    \begin{columns}
        \column{0.45\textwidth}
        \begin{center}
            \textbf{Causal Structure $\graph$}\\
            {\footnotesize (classical model)} \\
            \[ \graph = \br{\nodes, \edges} \]
            \vspace{-0.3in}
            \begin{align*}
                \edges &: \text{\term{causal influence}} \\
                \nodes &: \text{\term{random variables}} \\
                \nodes_{O} &: \text{\term{observable variables}} \\
                \nodes_{L} &: \text{\term{latent variables}}
            \end{align*}
            \[ \nodes = \nodes_{O} \cup \nodes_{L} \]
        \end{center}
        \column{0.45\textwidth}
        \begin{center}
            \textbf{Marginal Model $\prob^{\mscenario}$} \\
            {\footnotesize (observations)}
            \[ \mscenario : \text{\term{marginal scenario}} \]
            \[ \mscenario = \bc{V \mid V \subseteq \nodes_{O}} \]
            \[ \prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario} \]
        \end{center}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{The Triangle Scenario}
    \begin{center}
        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \textbf{Question:} Is $\prob^{\mscenario}$ \term{compatible} with $\graph$?\\
    \textbf{Answer:} If $\prob^{\mscenario}$ is to be compatible with $\graph$ then:
    \begin{enumerate}
        \item $\prob^{\mscenario}$ must admit a \term{joint distribution} $\prob[\nodes]$:
        \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
        \item $\prob[\nodes]$ must obey \term{Markov conditions}:
        \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
    \end{enumerate}
    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
\end{frame}

\begin{frame}
    \frametitle{Classical (Compatible) Distributions for Triangle Scenario}
    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Quantum Distributions for Triangle Scenario}
    \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Why Triangle Scenario?}
    \begin{itemize}
        \item Triangle scenario (TS) has be studied extensively before
        \item In~\cite{Branciard_2012} it was noted that characterizing quantum non-classicality in TS remained an \textbf{open problem} and that identifying compatibility inequalities \textbf{seemed challenging}
        \item In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which quantum non-classicality is manifest (proof without inequalities)
        \item In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)
        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have been unable to find inequalities with quantum violations
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Deriving Inequalities}
    \begin{itemize}
        \item Two necessary components to compatibility: joint distribution, Markov separability
        \item It is possible to cast Markov separability problem into a joint distribution problem (at least partially)!
        \item \term{Inflation Technique}\cref{Inflation} developed by E. Wolfe, R. Spekkens, T. Fritz provides tools for solving compatibility problem
        \item \term{Definite Extension Procedure} developed by myself, E. Wolfe and others allows one to derive inequalities for \textbf{very large} causal structures
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility Inequalities}
    \begin{gather*}
    P_{ABC}(000)P_{C}(3) \\
    \leq \\
    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) \\
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility Inequalities (Simplified)}
    \begin{gather*}
        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + \\
        P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
        \leq \\
        P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
        P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0)
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Uniform Noise}
    \[ \s{U}_{\varepsilon}\br{P} = \br{1 - \varepsilon} P + \varepsilon \s{U} \]
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    % \begin{center}
    %     \begin{tikzpicture}
    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
    %         \draw[] (1*\ts,0) node[]{$=$};
    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
    %         \draw[] (3*\ts,0) node[]{$+$};
    %         \draw[] (4*\ts,0) node[]{$\delta$};
    %     \end{tikzpicture}
    % \end{center}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{itemize}
        \item Quantum/Classical difference can be observed in the triangle scenario
        \item Successful demonstration of the inflation technique
        \item Developed new algorithmic tools to find such inequalities
        \item New measures of non-classicality which lead to new quantum mechanical resources
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Notation}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \begin{itemize}
        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        % \item Marginal scenario forms a \textit{simplicial complex}
        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
    \end{itemize}
    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
    \note[item]{Marginal scenario refers to the those sets of random variables}
    \note[item]{The complete set of random variables are the joint random variables}
\end{frame}

\begin{frame}
    \frametitle{Graph Theory}
    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
    \begin{itemize}
        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
    \end{itemize}
    Notation extends to sets of nodes $N \subseteq \nodes$,
    \begin{itemize}
        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
    \end{itemize}
    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
    \begin{enumerate}
        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
    \end{enumerate}
    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
\end{frame}

\begin{frame}
    \frametitle{Deriving Inequalities}
    Two necessary components to compatibility:
    \begin{enumerate}
        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
        \begin{itemize}
            \item Is the marginal model contextual or non-contextual?
            \item 3 distinct ways to tackle this problem
            \begin{enumerate}
                \item Convex hull, Polytope projection, Fourier-Motzkin
                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
                \item Linear Program Feasibility/Infeasibility
            \end{enumerate}
        \end{itemize}
        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \begin{itemize}
            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
        \end{itemize}
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Technique}
    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
        And '$\sim$' is a \term{copy-index} equivalence relation
        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma}
    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
    \begin{enumerate}
        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
        \item Construct \term{inflated causal parameters}
        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{itemize}
        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
    \end{itemize}
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    \begin{itemize}
        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{lemma}
        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    \end{lemma}
    \begin{corollary}
        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
    \end{corollary}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets}
    \begin{itemize}
        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
        \item A \term{pre-injectable set} $N'$:
        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Network Permutation Matrix}
    \begin{columns}
        \column{0.6\linewidth}
        \begin{itemize}
            \item States and measurements in the Triangle Scenario are not aligned
            \item Without $\netperm$, $\prob[ABC]$ would be separable
            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
            \item $\netperm$ is a $2^6 \times 2^6$ matrix
            \item Shifts one qubit to the left
        \end{itemize}
        \column{0.4\linewidth}
            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
    \end{columns}
    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
\end{frame}

\begin{frame}
    \frametitle{Outcomes and Events}
    \begin{definition}
        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
    \end{definition}
    \begin{definition}
        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
    \end{definition}
    \begin{definition}
        The set of events over the marginal contexts are the \term{marginal events}
        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Distribution Vectors}
    \begin{definition}
        The \term{joint distribution vector} $\probvec^{\jointvar}$
        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
    \end{definition}
    \begin{definition}
        The \term{marginal distribution vector} $\probvec^{\mscenario}$
        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
    \end{definition}
    Can now write complete marginal problem as matrix multiplication:
    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
\end{frame}

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item \term{Incidence matrix} $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m = j|_{\Dom{m}} \\
            0 & \text{otherwise}
        \end{cases} \]
        \begin{gather*}
        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
        \end{gather*}

\begin{frame}
    \frametitle{Causal Symmetry}
    \begin{itemize}
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
        \item Compatibility is independent of variable labels $I, \graph \to \varphi\bs{I}, \varphi\bs{\graph}$
        \item Need $\varphi\bs{\graph} = \graph$ to find new $\varphi\bs{I}$
    \end{itemize}
    \begin{definition}
        The \term{causal symmetry group} of causal structure $\graph$:
        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
        Strictly speaking, one needs to preserve observable nodes:
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
    \end{definition}
    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e. inequality) that is symmetric under exchange of parties}
    \note<1>[item]{Surprisingly, it is possible to do so!}
    \note<1>[item]{Here is how.}
    \note<1>[item]{First, we will formally define the symmetry group in question}
    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
\end{frame}

\begin{frame}
    \frametitle{Causal Symmetry and Inflation}
    \begin{itemize}
        \item Causal symmetry group for $\graph'$ is no good!
        \item Not possible to deflate inequality if it's not in terms of injectable sets
        \begin{definition}
            The \term{restricted causal symmetry group} $\Phi$ of $\graph'$:
            \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
        \end{definition}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Restricted Causal Symmetry of Large Inflation}
    \begin{itemize}
        \item $\Phi$ for the large inflation is an order $48$ group with $4$ generators
    \end{itemize}
    \begin{equation*}
    \begin{aligned}[c]
    &\hspace{1mm}\gep_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\gep_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\gep_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\gep_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Symmetric Incidence}
    \begin{itemize}
        \item Group orbits through repeated action of $\varphi \in \Phi$ on $m \in \Events{\mscenario}$ and $j \in \Events{\jointvar}$
    \end{itemize}
    \begin{align*}
        \Phi\bs{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \Phi} \\
        \Phi\bs{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \Phi}
    \end{align*}
    \begin{itemize}
        \item Construct \term{symmetric incidence matrix} $\Phi\bs{M}$
    \end{itemize}
    \[ \Phi\bs{M}_{\Phi\bs{m}, \Phi\bs{j}} = \sum_{m' \in \Phi\bs{m}}\sum_{j' \in \Phi\bs{j}} M_{m',j'} \]
    \[ \Phi\bs{M} = \La_{\Phi\bs{\Events{\mscenario}}}\tcdot M \tcdot \La_{\Phi\bs{\Events{\jointvar}}} \]
    \begin{itemize}
        \item $\Phi\bs{M}$ not a bit-wise matrix like $M$
        \item For large inflation $M$ is $16,896 \times 16,777,216$
        \item For large inflation $\Phi\bs{M}$ is $450 \times 358,120$ % 3566922 entries
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Symmetrized Fritz}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/symmetrized_fritz.pdf}
    \end{center}
    \begin{itemize}
        \item More non-local yet not quantum-accessible
        \item Quantum-accessible distributions form non-context set
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing POVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
        \item $n$-outcome measurement
        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
        \item Warrants consideration of \term{projective-valued measures (PVMs)}
    \end{itemize}
    \note<1>[item]{Naimark's Dilation Theorem}
\end{frame}
